---
title: "Cabbages"
author: "Roselyn Villatoro"
date: "Fall 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$: There is no difference in the average VitC content between c39 and c52 cultivation methods.

$H_A$:There is a difference in the average VitC content between c39 and c52 cultivation methods.

# Methods
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

VitC ~ cultivation method
VitC is an integer which makes it numerical.
Cultivation is a factor which makes it categorical.
Which means you upload the Numerical~Cat file.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

The Graphical Descriptive Results show us the difference between VitC and cult. It shows us that the VitC in c39 is less than c52.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The average of VitC content in c39 is 51.5.
The average of VitC content in c52 is 64.4

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The inferential results shows that the p-value is .00000003, which is less than 0.05 so we reject the null hypothesis and conclude that c52 is better than c39 for VitC cultivation. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We looked at the difference between VitC and cult in the boxplots, which showed us that c39 is less than c52.And in the numerical results we saw that the average of VitC content in c39 is 51.5 and in c52 it's 64.4. Then in inferential results we saw that the p-value is .00000003405.We reject the null hypothesis because the p-value is lower than 0.05.We have evidence that there is a difference in the VitC content, which shows that c52 is better than c39 cultivation methods.
